The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-13 article.tex
reorganized and added things

The remainder of the paper will continue as follows. Related work pertaining to integrity, availability, and confidentiality will be presented in \ref{sec:Related Work}. The system design is introduced in section \ref{sec:Methodology} which further discusses the implementation techniques used. We then demonstrate our experiments in section \ref{Results} and the results obtained in section \ref{Results} and gather a conclusion from the results and motivation of the paper in section \ref{Conclusion}.

@@

New agent authentication work in a similar manner to normal communication but must be initiated by the party with the appropriate and working CR pair. Last but not least, this communication must be implemented like a tunnel where each agent can be uniquely identified by the system.

@@

A KD tree is used on both maps to find the closest approximate points to each mean found. The few particles gathered by this process are used, by the compromised and uncompromised maps, to form Probability Density Function (PDF) by means of a Kernel Density Estimation (KDE). 
\begin{equation}
 P(c,b|s) =\frac {(P(b,s|c)P(c)} {(P(b,s|c)P(c) + 
 P(b,s|c' )P(c' ))} 
 \label{fig:Bayes}
\end{equation}
This distribution is used to obtain the probability the mean of the particle filter approximation falls within each map. The product of these two probability biases the input to the next iteration to the Bayes equation \ref{fig:Bayes} where b = behavior of the robot, s = state of the robot and c = the probability the robot is compromised \cite{Thrun2002Probabilistic}. This implementation provides a way for the change in behavior to impact the current belief.

@@

We begin by defining our state and control in \autoref{abs_st_ctr_table}. Position and velocity are included in the state in order to make future conjectures about the behavior of the robot.

\begin{table}[] \label{abs_st_ctr_table} \caption{Implemented state and control}
\begin{center}
\begin{tabular}{|c|c|}
\hline
State & Control\\
\hline
$x,y,\theta,v_f,v_\theta$ & $a_f,a_\theta$\\
\hline
\end{tabular}
\end{center}
\end{table}

In order to account for extreme table sizes the table can be kept outside of the secure hardware and be encrypted by the hardware key.

In order to keep the agent to agent principle we render the IP layer of communication unfit and utilize a more conservative approach of omitting the IP layer to the network stack.

Use of the data link layer pushed the use of raw sockets; the socket class for python was used instead. The downside however remains in that the socket class requires sudo, or root, access in order to run the node since permissions do not allow sockets to be ran under a regular user. Since giving admin privileges to a node can be considered a threat, there is push to either change the permissions for saw sockets or to change to a new library all together.

The python code was first loaded onto two different laptops, both running Ubuntu 14.04 LTS with a full ROS install, and connectivity was established. We first start with obtaining the database from the 'central base' module created as seen in figure~\ref{fig:TopicIntr1}. The directory where the database file resided was located and moved to the correct agent where the robot\_proxy was executed.

\begin{figure}[]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr1}
\caption{The initial communication with the central frame is made here. Each database, in its encrypted form, is created to be placed with each corresponding agent.}
\label{fig:TopicIntr1}
\end{figure}

A new connection is detected and notified via a list in topic /Host\_lists which signifies a working connection. Now, in order to test the appropriate data the testing node Simple\_calc.py was used as seen in Figure~\ref{fig:TopicIntr2}.

\begin{figure}[]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr2}
\caption{Topic Interaction with node- As new agents are populated, the external host lists are updated. Hence, when the topic handler retrieves the Host Lists from all the connection objects, the nodes in the current system will have an accurate overview of which topics are being published elsewhere based on the MAC of each external agent.}
\label{fig:TopicIntr2}
\end{figure}

@@

@@

\begin{table}[] \label{st_ctr_table}
\begin{center}
\begin{tabular}{|c|c|}
\hline
State & Control\\
\hline
$x,y,\theta,v_f,v_\theta$ & $a_f,a_\theta$\\
\hline
\end{tabular}
\end{center}
\end{table}

\section{Results} \label{Results}
\subsection{Secure Ad-Hoc Channel Communication}

>>>>

The remainder of the paper will continue as follows. Related work pertaining to integrity, availability, and confidentiality will be presented in \autoref{sec:Related Work}. The system design is introduced in section \autoref{sec:Methodology} which further discusses the implementation techniques used. We then demonstrate our experiments in section \autoref{Results} and the results obtained in section \autoref{Results} and gather a conclusion from the results and motivation of the paper in section \autoref{Conclusion}.

@@

New agent authentication work in a similar manner to normal communication but must be initiated by the party with the appropriate and working CR pair. In order to account for extreme table sizes the table can be kept outside of the secure hardware and be encrypted by the hardware key.

@@

A KD tree is used on both maps to find the closest approximate points to each mean found. The few particles gathered by this process are used, by the compromised and uncompromised maps, to form Probability Density Function (PDF) by means of a Kernel Density Estimation (KDE). 
\begin{equation}
 P(c,b|s) =\frac {(P(b,s|c)P(c)} {(P(b,s|c)P(c) + 
 P(b,s|c' )P(c' ))} 
 \label{fig:Bayes}
\end{equation}
This distribution is used to obtain the probability the mean of the particle filter approximation falls within each map. The product of these two probability biases the input to the next iteration to the Bayes equation \autoref{fig:Bayes} where b = behavior of the robot, s = state of the robot and c = the probability the robot is compromised \cite{Thrun2002Probabilistic}. This implementation provides a way for the change in behavior to impact the current belief.

@@

In order to keep the agent to agent principle we render the IP layer of communication unfit and utilize MAC addressing directly, omitting the IP layer to the network stack. Use of the data link layer pushed the use of raw sockets; the socket class for python was used instead. The socket class required root access in order to run the node since permissions do not allow sockets to be ran under a regular user. Since giving admin privileges to a node can be considered a threat, there is push to either change the permissions for saw sockets or to change to a new library all together in future work.

The python code was loaded onto two Zedboards and a laptop, all running Ubuntu 14.04 LTS with a full ROS install, and connectivity was established. We first start with obtaining the database from the 'central base' module created as seen in figure~\autoref{fig:TopicIntr1}. The directory where the database file resided was located and moved to the correct agent where the robot\_proxy was executed.

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr1}
\caption{The initial communication with the central frame is made here. Each database, in its encrypted form, is created to be placed with each corresponding agent.}
\label{fig:TopicIntr1}
\end{figure}

A new connection is detected and notified via a list in topic /Host\_lists which signifies a working connection. Now, in order to test the appropriate data the testing node Simple\_calc.py was used as seen in Figure~\autoref{fig:TopicIntr2}.

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{TopicIntr2}
\caption{Topic Interaction with node- As new agents are populated, the external host lists are updated. Hence, when the topic handler retrieves the Host Lists from all the connection objects, the nodes in the current system will have an accurate overview of which topics are being published elsewhere based on the MAC of each external agent.}
\label{fig:TopicIntr2}
\end{figure}

@@

\subsection{State Estimation}
We begin by defining our state and control in \autoref{abs_st_ctr_table}. Position and velocity are included in the state in order to make future conjectures about the behavior of the robot.

\begin{table}[h] \label{abs_st_ctr_table} \caption{Implemented state and control}
\begin{center}
\begin{tabular}{c|c}
State & Control\\
\hline
$x,y,\theta,v_f,v_\theta$ & $a_f,a_\theta$\\
\end{tabular}
\end{center}
\end{table}

\section{Results} \label{Results}
After the implementation previously mentioned several metrics were taken on the three components developed.

\subsection{Secure Ad-Hoc Channel Communication}
Band width measurements were conducted via a sample node using the payload obtained at the final destination. That is, \autoref{bandwith_one} demonstrates the effective bandwidth when only two agents connected at the same time.

\autoref{bandwidth_two} provides a look at the scenario were there is much traffic in the medium of connection itself.

@@

\subsection{State Detection}
To verify the system's functionality the first set of results with no particle filter and noiseless data being received can be seen by \autoref{stat_dect_one}.

The more interesting view however is that of \autoref{stat_dect_two} where by the particle filter is introduced and the position is not given from exact data but the state estimation itself.
